Illustration: Feature Based Time Series Clustering in Psychology [tsFeatureClustR]

### 2023-08-11 tutorial/02-feature-extraction.qmd
tutorial update

The selection of time series features should always be driven by the research questions and field-specific conventions, but for our illustration we chose six time series features that relate to common psychological research questions and recent works within the field: (1) central tendency, (2) variability, (3) instability, (4) self-similarity, (5) linear trend, and (6) nonlinearity. We provide the `featureExtractor()` function to extract a number of measurements for each time series aspect. The function is also available as part of the R package that bundles a number of functions we used for the illustration ([Download the R package here](https://github.com/JannisCodes/tsFeatureExtracR/archive/refs/tags/v.0.1.0.tar.gz)). The time series feature operationalizations we chose for our illustration here are marked in bold.

>>>>

::: {.grid}

::: {.g-col-4}
[![](images/logo_tsfeatureextractr.png)](https://github.com/JannisCodes/tsFeatureExtracR)
[Download the R package here](https://tsfeatureclustr.com/assets/tsFeatureExtracR_0.1.0.tar.gz)
:::

::: {.g-col-8}
The selection of time series features should always be driven by the research questions and field-specific conventions, but for our illustration we chose six time series features that relate to common psychological research questions and recent works within the field: (1) central tendency, (2) variability, (3) instability, (4) self-similarity, (5) linear trend, and (6) nonlinearity. We provide the `featureExtractor()` function to extract a number of measurements for each time series aspect. The function is also available as part of the R package that bundles a number of functions we used for the illustration. 
:::

:::

The time series feature operationalizations we chose for our illustration here are marked in bold.

### 2023-08-11 tutorial/about.qmd
tutorial update

The full code of this illustration as well as the main manuscript is available as part of [our GitHub repository](https://github.com) [@KreienkampMasked-clust-github]. A minimal version of the code as well as an archive file are available in [our Open Science repository](https://osf.io/j8dzv/?view_only=c765efa51e6545e588b29999611eb789) [@KreienkampMasked-clust-osf]. For convenience purposes, we have also collected a number of functions we created as part of the illustration as an R-package. This package is available as its own GitHub repository and can be downloaded with the `devtools` package `devtools::install_github("JannisCodes/tsFeatureExtracR")`, you can also [download the R package here](https://github.com/JannisCodes/tsFeatureExtracR/archive/refs/tags/v.0.1.0.tar.gz) [@KreienkampBlinded2023-tsFeatureExtracR].

>>>>

The full code of this illustration as well as the main manuscript is available as part of [our GitHub repository](https://github.com) [@KreienkampMasked-clust-github]. A minimal version of the code as well as an archive file are available in [our Open Science repository](https://osf.io/j8dzv/?view_only=c765efa51e6545e588b29999611eb789) [@KreienkampMasked-clust-osf]. For convenience purposes, we have also collected a number of functions we created as part of the illustration as an R-package. This package is available as its own GitHub repository and can be downloaded with the `devtools` package `devtools::install_github("JannisCodes/tsFeatureExtracR")`, you can also [download the R package here](https://tsfeatureclustr.com/assets/tsFeatureExtracR_0.1.0.tar.gz) [@KreienkampBlinded2023-tsFeatureExtracR].

### 2023-08-11 tutorial/index.qmd
tutorial update

---
title: "Illustration: Feature Based Time Series Clustering in Psychology [tsFeatureExtracR]"
author:
  - name: Masked for Peer Review
  - name: ██████ ██████████
    orcid: 0000-0000-0000-0000
  - name: ██████████ ████████
    orcid: 0000-0000-0000-0000
  - name: ███ ██████
    orcid: 0000-0000-0000-0000
  - name: ███ ███████
    orcid: 0000-0000-0000-0000
  - name: █████ ██ █████
    orcid: 0000-0000-0000-0000
  - name: █████ ██ █████████
    orcid: 0000-0000-0000-0000
  # - name: Jannis Kreienkamp
  #   orcid: 0000-0002-1831-5604
  #   email: j.kreienkamp@rug.nl
  #   corresponding: true
  #   # affiliations:
  #   #   - ref: rug
  # - name: Maximilian Agostini
  #   orcid: 0000-0001-6435-7621
  #   # affiliations:
  #   #   - ref: rug
  # - name: Rei Monden
  #   orcid: 0000-0003-1744-5447
  #   # affiliations:
  #   #   - ref: hu
  # - name: Kai Epstude
  #   orcid: 0000-0001-9817-3847
  #   # affiliations:
  #   #   - ref: rug
  # - name: Peter de Jonge
  #   orcid: 0000-0002-0866-6929
  #   # affiliations:
  #   #   - ref: rug
  #   #   - ref: icpe
  # - name: Laura F. Bringmann
  #   orcid: 0000-0002-8091-9935
  #   # affiliations:
  #   #   - ref: rug
  #   #   - ref: icpe
# affiliations:
#   - id: rug
#     name: University of Groningen
#   - id: hu
#     name: Hiroshima University
#   - id: icpe
#     name: ICPE
---

>>>>

---
title: "Illustration: Feature Based Time Series Clustering in Psychology [tsFeatureClustR]"
author:
  - name: Masked for Peer Review
  - name: ██████ ██████████
    orcid: 0000-0000-0000-0000
  - name: ██████████ ████████
    orcid: 0000-0000-0000-0000
  - name: ███ ██████
    orcid: 0000-0000-0000-0000
  - name: ███ ███████
    orcid: 0000-0000-0000-0000
  - name: █████ ██ █████
    orcid: 0000-0000-0000-0000
  - name: █████ ██ █████████
    orcid: 0000-0000-0000-0000
  # - name: Jannis Kreienkamp
  #   orcid: 0000-0002-1831-5604
  #   email: j.kreienkamp@rug.nl
  #   corresponding: true
  #   # affiliations:
  #   #   - ref: rug
  # - name: Maximilian Agostini
  #   orcid: 0000-0001-6435-7621
  #   # affiliations:
  #   #   - ref: rug
  # - name: Rei Monden
  #   orcid: 0000-0003-1744-5447
  #   # affiliations:
  #   #   - ref: hu
  # - name: Kai Epstude
  #   orcid: 0000-0001-9817-3847
  #   # affiliations:
  #   #   - ref: rug
  # - name: Peter de Jonge
  #   orcid: 0000-0002-0866-6929
  #   # affiliations:
  #   #   - ref: rug
  #   #   - ref: icpe
  # - name: Laura F. Bringmann
  #   orcid: 0000-0002-8091-9935
  #   # affiliations:
  #   #   - ref: rug
  #   #   - ref: icpe
# affiliations:
#   - id: rug
#     name: University of Groningen
#   - id: hu
#     name: Hiroshima University
#   - id: icpe
#     name: ICPE
---
